What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-15 Manuscript/MS- What is LDD.tex
Added DRYAD ref.

@@

This review does not use new raw data, but includes some re-analyses of previously published material. All the original data supporting the paper, R code, supplementary figures, and summaries of analytical protocols is available at the author's GitHub repository (\texttt{https://github.com/pedroj/MS\_LDD}), with DOI: \texttt{\#/zenodo.\#}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

This review does not use new raw data, but includes some re-analyses of previously published material. All the original data supporting the paper, R code, supplementary figures, and summaries of analytical protocols is available at the author's GitHub repository (\texttt{https://github.com/pedroj/MS\_LDD}), and also deposited in the Dryad repository \citep{Jordano:2016ab}: \\\texttt{http://datadryad.org/resource/doi:10.5061/dryad.k0v67}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
